Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-14 paper.tex
Tighten up first three paragraphs; resolves #45

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however,
there still is concern at which scale an experiment must be performed to be
relevant to full-scale application. One might obtain different predictions for
scaled systems due to modified physics at lower Reynolds numbers, e.g., laminar
boundary layers and transitional flow regimes. If the numerical model is then
considered ``validated,'' there is a risk that its application at full-scale may
produce incorrect predictions. As such, it is questionable whether numerical
models validated with physical model data obtained at Reynolds numbers orders of
magnitude away from prototype scale should be considered validated at all.

Uncertainty from scale effects can potentially be overcome by showing that a
scaled physical model test has become Reynolds number independent, and therefore
validation efforts should be relevant at full scale. It is therefore of interest
how small---since physical model size or facility flow speed generally correlate
with cost---the model can be while remaining a reliable predictor of full-scale
behavior. At the very least, it is necessary to test at a scale where results
can be extrapolated, i.e., changes are occurring quasi-linearly without dramatic
changes in the underlying physical principles governing the behavior of
interest, e.g., power production in the case of a wind or MHK turbine.

>>>>

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however,
there still is concern at which scale an experiment must be performed to be
relevant to full-scale application. Similarly, it is questionable whether
numerical models validated with physical model data obtained orders of magnitude
away from prototype scale should be considered validated at all.
